Estimating the Financial Impact of Wildfire Smoke on US National parks

### 2020-05-21 Markdown Documents/Manuscript.Rmd
Small plot anotation change

```{r echo=FALSE, cache=TRUE, warning=FALSE, message=FALSE, fig.height = 6, fig.width = 12}
dat%>%filter(UnitCode %in% fitsig$Par)%>%group_by(ParkName)%>%
  summarise(totrec=sum(RecreationVisits),totpred=sum(PredNoSmoke50CI))%>%ungroup()%>%
  mutate(diff=totpred-totrec)%>%
ggplot(., 
       aes(y = reorder(ParkName,diff),
           x = totrec,
           xend = totpred)) +  
  ggalt::geom_dumbbell(size = 1.2,
                       size_x = 5, 
                       size_xend = 5,
                       colour = "darkgrey", 
                       colour_x = "black", 
                       colour_xend = "#1f78b4",dot_guide = T,dot_guide_size = NULL,dot_guide_colour = "lightgrey") +
  scale_x_continuous( breaks=seq(10000000,90000000,20000000),labels = scales::comma) + 
  labs(title = "Total Lost Visitation",
       subtitle = "1980 to 2018",
       x = "Total Visits",
       y = "")+theme_classic()+mytheme

>>>>

```{r echo=FALSE, cache=TRUE, warning=FALSE, message=FALSE, fig.height = 6, fig.width = 12}
dat%>%filter(UnitCode %in% fitsig$Par)%>%group_by(ParkName)%>%
  summarise(totrec=sum(RecreationVisits),totpred=sum(PredNoSmoke50CI))%>%ungroup()%>%
  mutate(diff=totpred-totrec)%>%
ggplot(., 
       aes(y = reorder(ParkName,diff),
           x = totrec,
           xend = totpred)) +  
  ggalt::geom_dumbbell(size = 1.2,
                       size_x = 5, 
                       size_xend = 5,
                       colour = "darkgrey", 
                       colour_x = "black", 
                       colour_xend = "#1f78b4",dot_guide = T,dot_guide_size = NULL,dot_guide_colour = "lightgrey") +
   annotate("text", x = 60000000, y = "Yosemite NP", label = "Observed visitation",vjust=-1,hjust=1)+
  annotate("text", x = 73000000, y = "Yosemite NP", label = "Predicted visitation no smoke",vjust=-1)+
  scale_x_continuous( breaks=seq(10000000,90000000,20000000),labels = scales::comma) + 
  labs(title = "Total Lost Visitation",
       subtitle = "1980 to 2018",
       x = "Total Visits",
       y = "")+theme_classic()+mytheme+theme(plot.subtitle = element_text(face = "bold"))
